\cvevent{Senior Product Manager}{Plaid}{01/20/2021 -- Preent}{San Franscisco, California}
\begin{itemize}
\item Led the development and launch of a new financial data integration platform, increasing market penetration by 25\% within the first year.
\item Managed a cross-functional team of 10, including engineers and designers, to deliver the project on time and under budget.
\item Implemented a customer feedback loop that resulted in a 40\% improvement in customer satisfaction scores.
\item Conducted competitive analysis to inform product positioning, leading to a 15\% increase in product adoption.
\item Negotiated partnerships with key financial institutions, expanding the platform's reach and functionality.
\item Developed and executed a go-to-market strategy that resulted in the product being featured in major tech publications.
\end{itemize}

\divider

\cvevent{Product Manager}{Stripe}{06/2018 -- 12/2020}{San Franscisco, California}
\begin{itemize}
\item Oversaw the development of a new payment processing feature, resulting in a 20% increase in transaction volume.
\item Collaborated with the engineering team to streamline the development process, reducing time to market by 30%.
\item Led user research initiatives that informed product improvements, enhancing user experience and satisfaction.
\item Managed product backlog and prioritization, ensuring alignment with strategic business goals.
\item Facilitated cross-departmental communication to align product development with marketing and sales strategies.
\end{itemize}

\divider

\cvevent{Associate Product Manager}{Salesforce}{03/2026 -- 05/2018}{San Franscisco, California}
\begin{itemize}
\item Contributed to the development of a CRM feature that increased user engagement by 30%.
\item Assisted in conducting market research and analysis to guide product development strategies.
\item Supported senior product managers in roadmap planning and execution.
\item Participated in agile development processes, contributing to sprint planning and review meetings.
\end{itemize}
